AtmoSwing (v1.4): Analog Technique Model for Statistical weather forecastING

### 2015-10-13 AtmoSwing - Geoscientific Model Development/template.tex
Moving content from the optimization paper to the AtmoSwing one.

%% Version 4.3.2, 25 August 2014
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template.tex --  LaTeX-based template for submissions to the 
% American Meteorological Society
%
% Template developed by Amy Hendrickson, 2013, TeXnology Inc., 
% amyh@texnology.com, http://www.texnology.com
% following earlier work by Brian Papa, American Meteorological Society
%
% Email questions to latex@ametsoc.org.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PREAMBLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Start with one of the following:
% DOUBLE-SPACED VERSION FOR SUBMISSION TO THE AMS
\documentclass{ametsoc}

% TWO-COLUMN JOURNAL PAGE LAYOUT---FOR AUTHOR USE ONLY
%\documentclass[twocol]{ametsoc}

\usepackage{multirow}
\usepackage{gensymb}
\usepackage{subcaption}
\usepackage{xcolor,colortbl}

% After http://tex.stackexchange.com/questions/94799/how-do-i-color-table-columns-and-rows
\newcommand{\mc}[2]{\multicolumn{#1}{c}{#2}}
\definecolor{Gray}{gray}{0.85}
\definecolor{LightCyan}{rgb}{0.88,1,1}
\newcolumntype{a}{>{\columncolor{Gray}}c}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% To be entered only if twocol option is used

\journal{jcli}

%  Please choose a journal abbreviation to use above from the following list:
% 
%   jamc     (Journal of Applied Meteorology and Climatology)
%   jtech     (Journal of Atmospheric and Oceanic Technology)
%   jhm      (Journal of Hydrometeorology)
%   jpo     (Journal of Physical Oceanography)
%   jas      (Journal of Atmospheric Sciences)	
%   jcli      (Journal of Climate)
%   mwr      (Monthly Weather Review)
%   wcas      (Weather, Climate, and Society)
%   waf       (Weather and Forecasting)
%   bams (Bulletin of the American Meteorological Society)
%   ei    (Earth Interactions)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Citations should be of the form ``author year''  not ``author, year''
\bibpunct{(}{)}{;}{a}{}{,}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% To be entered by author:

%% May use \\ to break lines in title:

\title{Global Optimization of the Analogue Method by Means of Genetic Algorithms}

%%% Enter authors' names, as you see in this example:
%%% Use \correspondingauthor{} and \thanks{Current Affiliation:...}
%%% immediately following the appropriate author.
%%%
%%% Note that the \correspondingauthor{} command is NECESSARY.
%%% The \thanks{} commands are OPTIONAL.

    %\authors{Author One\correspondingauthor{Author One, 
    % American Meteorological Society, 
    % 45 Beacon St., Boston, MA 02108.}
% and Author Two\thanks{Current affiliation: American Meteorological Society, 
    % 45 Beacon St., Boston, MA 02108.}}

\authors{Pascal Horton\correspondingauthor{Terranum, Rue de l'industrie 35 bis, 1030 Bussigny, Switzerland.}}

%% Follow this form:
    % \affiliation{American Meteorological Society, 
    % Boston, Massachusetts.}

\affiliation{University of Lausanne and Terranum, Lausanne, Switzerland}

%% Follow this form:
    %\email{latex@ametsoc.org}

\email{pascal.horton@alumnil.unil.ch}

%% If appropriate, add additional authors, different affiliations:
    %\extraauthor{Extra Author}
    %\extraaffil{Affiliation, City, State/Province, Country}

\extraauthor{Michel Jaboyedoff}
\extraaffil{University of Lausanne, Lausanne, Switzerland}

%% May repeat for a additional authors/affiliations:

%\extraauthor{}
%\extraaffil{}

\extraauthor{Charles Obled}
\extraaffil{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%
% Enter your abstract here
% Abstracts should not exceed 250 words in length!
%
% For BAMS authors only: If your article requires a Capsule Summary, please place the capsule text at the end of your abstract
% and identify it as the capsule. Example: This is the end of the abstract. (Capsule Summary) This is the capsule summary.

\abstract{The analogues method is based on a statistical relationship between synoptic atmospheric variables and local weather, which we aim at forecasting. This relationship is expressed through many parameters that are usually calibrated by means of a semi-automatic procedure. This classic calibration is relatively fast and provide acceptable results, but it has strong constraints, is made of successive steps and thus cannot handle parameters dependencies, and mainly, it cannot calibrate automatically some parameters, such as the selection of the pressure levels and the temporal windows on which the predictors are compared. In order to surpass these limitations, we assessed a global optimization technique, namely genetic algorithms, that can optimize jointly all parameters of the method and thus provide a global optimum by taking into account the parameters dependencies. Moreover, it can calibrate parameters that were previously manually assessed, and can take into account new degrees of freedom that were unthinkable before. 
These kind of optimization techniques need however to be tailored to the problem to solve. We had to assess multiple combinations of algorithms, and even to develop new operators, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of genetic algorithms to optimize the analogue method. These recommendations are the primary outcome of this work, as it opens new perspective for the improvement of the analogue method, and its application to new regions or to new predictands.
We then applied the optimizer to the Rh\^{o}e catchment in the Swiss Alps and obtained coherent results which significantly improve the performance of the forecasting by analogy. The optimizer allowed us to calibrate jointly all parameters of the method and to add a weighting of the criteria per pressure level, as well as non-overlapping spatial windows.}

@@

%% Necessary!
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MAIN BODY OF PAPER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

%% In all cases, if there is only one entry of this type within
%% the higher level heading, use the star form: 
%%
% \section{Section title}
% \subsection*{subsection}
% text...
% \section{Section title}

%vs

% \section{Section title}
% \subsection{subsection one}
% text...
% \subsection{subsection two}
% \section{Section title}

%%%
% \section{First primary heading}

% \subsection{First secondary heading}

% \subsubsection{First tertiary heading}

% \paragraph{First quaternary heading}

\section{Introduction}
\label{section_intro}

The analogue method is a downscaling technique based on the idea expressed by \citet{Lorenz1969}, that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Bontron2005}. It aims at forecasting a predictand, often the daily precipitation, on the basis of predictor variables describing the synoptic atmospheric circulation. Many parameters define this relationship, which are usually calibrated by means of a semi-automatic procedure.

\subsection{The analogue method}
\label{section_analog_method}

Multiple variations of the methods exist, and some aspects and parameters will not be detailed hereafter. There are mainly 2 parametrizations that are used most often: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on humidity variables \citep{Obled2002, Bontron2005, Marty2012}.

The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table:params_R1}): We assess the similarity of the atmospheric circulation of a target date with every day of the archive by processing the S1 criteria \citep[Eq.\ (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window. \citet{Bontron2005} showed that the geopotential height at 500~hPa and 1000~hPa are the best first predictors of the NCEP/NCAR reanalysis dataset, and that the S1 criteria performs better than scores based on absolute distances. The reason for such better results is that the S1 criteria allows comparing the circulation pattern, by means of the gradients, rather than the absolute value of the geopotential height. To cope with seasonal effects, candidate dates are extracted within a period of 4 months centred around the target date, for every year of the archive.

\begin{equation}
\label{eq:S1}
S1=100 \frac {\displaystyle \sum_{i} \vert \Delta\hat{z}_{i} - \Delta z_{i} \vert}
{\displaystyle \sum_{i} max\left\lbrace \vert \Delta\hat{z}_{i} \vert , \vert \Delta z_{i} \vert \right\rbrace }
\end{equation}
where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points in the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation. The differences are processed separately in both directions. The smaller the S1 values are, the more similar the pressure fields.

The $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day. The number of analogues, $N_{1}$, is a parameter to calibrate. Then, the daily observed precipitation amount of the $N_{1}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.

The other most know parametrization adds a second level of analogy on humidity variables (Table \ref{table:params_R2}). The predictor that \citet{Bontron2004} found optimal for the France territory is a humidity index made of the product of the precipitable water with the relative humidity at 850~hPa. \cite{Horton2012a} confirmed that this index is better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis considered independently. When adding a second level of analogy, we subsample $N_{2}$ dates in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations. When we add a second level of analogy, we keep a higher number of analogues on the first level.

\subsection{Data}
\label{section_data}

The analogue method relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series we want to forecast.

Predictors are generally reanalysis datasets (and outputs of a global numerical weather prediction models for the target situation in operational forecasting, which is not the topic of this paper). We will work here with the NCEP/NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996}, but it can be any other reanalysis dataset.

The predictand (which is to be predicted) is in our case the daily precipitation (6~a.m. to 6~a.m. the next day) measured at the MeteoSwiss' stations network, for the period 1961-2008. The time series from every available gauging station were averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.

@@

@@

\subsection{Motivation for a global optimization}

The classic calibration is fast to optimize one spatial window for a given pressure level and temporal window. However, it doesn't provide an objective selection of the pressure level and temporal window. The only option is to try systematically every combination, which may be acceptable for no more than 2 levels. However, \citet{Horton2012a} showed that additional pressure levels may improve the method.

We observed during the calibration of the analogue method that the resulting parameters vary with the initial choices (such as the number of analogues). In addition, the different levels of analogy (eg on the atmospheric circulation and the humidity index) are always calibrated sequentially. However, we can not exclude any dependency between them, which could lead us to select another parametrization if we calibrate them together. Simultaneous calibration of all parameters has never been undertaken so far. Only a global optimization technique can be able to optimize all parameters of all analogy levels simultaneously.

When creating the classic calibration procedure, \citet{Bontron2004} was aware of the problem of dependencies between parameters and wrote: '' \textit{We perceive here the combinatorial aspect of our problem: variables and spatial windows are not independent. We will present our results by first searching the best variable [note: e.g. selection of the pressure level and the temporal window for the geopotential height] on a chosen spatial window, and next, the best window for the chosen variable. However, even by repeating the process, are we sure to obtain the optimal combination?} ''. And later in his work: '' \textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution} ''. \citet{Bliefernicht2010} has also faced the combinatorial issue of the parameters of the analogue method and concludes that one needs to be an expert to know their respective influence, their sensitivity and their nonlinear interactions. \citet{BenDaoud2010}, when calibrating the analogue method, also stated that '' \textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously } ''.

The analogue method needs to be adapted to every new region it is applied, because the leading meteorological influences are specific to this region. Even the selection of the pressure level and the temporal window should be reconsidered, when not the variable itself. For example, \citet{BenDaoud2010} found the vertical velocity relevant for the great plains in France, when \citet{Horton2012a} found no interest in this variable in an Alpine environment, because in the Alps, the vertical motion is mainly controlled by orographic effects, and was thus already well related to the atmospheric circulation itself. So, when adapting the analogue method to a new region, we should assess systematically every combination of pressure levels, time and spatial windows, which is an intensive task. This procedure can be automatized by a global optimization technique.

Our ambition was then to assess the feasibility of an automatic optimization of the analogue method through various techniques. The objective was to find an approach to optimize all parameters simultaneously, and thus be able to identify the global optimum in the parameter space. In addition, it can overcome the systematic manual assessments of certain parameters such as the selection of the pressure levels and time windows. Finally, it can open new perspectives by allowing the addition of new degrees of freedom, such as a weighting of the criteria values between the pressure levels, and the consideration of non-overlapping spatial windows between the pressure levels.

\citet{Horton2012a} assessed the ability of the \citet{Nelder1965a} method based on a simplex approach. This technique didn't provide satisfying results and failed at identifying the global optimum. Indeed, the results didn't converge and many local optimums came out. The parameter space of the analogue method is very complex and not appropriate for a linear optimization technique. Genetic algorithms were found to be much more relevant for such application.

\section{Adjusting genetic algorithms}

@@

\section{Example case study}

The analogue method has to be adapted to every new location it is applied. We improved the analogue method for the Swiss Alps, by means of genetic algorithms. A summary of the main results are provided here \citep[see][for the details]{Horton2012a}. Even though the results may differ from one place to another, the applicability of GAs to the analogue method remains universal.

\subsection{Case study description}

The study area is the alpine upper Rh\^{o}ne catchment in Switzerland (Fig.\ \ref{fig:map}). The altitude ranges from 372 to 4634~m.a.s.l.\ and the area is 5524~km$^{2}$. This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at providing a real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}. Even thought the region is rather small, the meteorological influences related to extreme weather conditions varies substantially within it \citep[see][]{Horton2012}. Based on different climatological analyses, the gauging stations in the catchment were clustered in 10~subregions (Fig.\ \ref{fig:map}) :

\begin{enumerate}
	\setlength\itemsep{-4px}
	\item Swiss Chablais
	\item Trient Valley
	\item West Bernese Alps
	\item Lower Rhone Valley
	\item Left side valleys
	\item Southern ridges
	\item Upper Rhone Valley
	\item Southeast ridges
	\item East Bernese Alps
	\item Conches Valley
\end{enumerate}

The 48 years precipitation dataset (see section \ref{section_intro}.\ref{section_data}) was divided into a calibration period and a validation period. Using data independent from the calibration period to validate our results is very important in order to assess the robustness of the improvements and to avoid overparametrization of the method.

In order to reduce potential bias related to trends in the climate change or to the evolution in measurement techniques, the selection of the validation period is evenly distributed over the entire series \citep{BenDaoud2010}. Thus, we selected one year every six years for validation, which represents a total of 8 years for the validation and 40 for calibration. The choice of the sequence was made in order to have similar statistical characteristics between the calibration and the validation periods.

\subsection{Optimization of the analogy of atmospheric circulation}

We first optimized the analogy of atmospheric circulation alone, without humidity variables, for our 10 subregions. We started from the most simple analogue method, and increased the complexity in order to identify the degrees of freedom that are of particular interest. Thus, the tested parametrization evolved iteratively in complexity. We do not provide the detailed results of the intermediate stages \citep[see][for the details]{Horton2012a}, but only the main conclusions.

We first considered the reference method for the analogy of the atmospheric circulation, based on the 500 and 1000~hPa levels. We let the optimizer choose the number of analogues, both spatial windows with no overlapping constraint, as well as the temporal window (hours of observation of the geopotential). The classic calibration cannot automatically choose the temporal window, neither handle non-overlapping spatial windows, and finally it cannot optimize all parameters simultaneously. With these improvements, we could gain a relative improvement of the CRPSS of 3.97\% and 2.45\% in average for the calibration and the validation periods respectively. Some tests showed that most of the gains are due to the non-overlapping spatial windows.

Then, we provided an additional degree of freedom to the AGs by letting them choose the pressure levels along with the other parameters. Evaluation of pressure levels is also a non-automated process in the classic calibration. We could observe that this degree of freedom increases the optimization time and may decrease the number of simulations that converge to a single solution. However, most solutions were very close in terms of score. The averaged relative improvement of the CRPSS is 5.63\% for the calibration and 3.82\% for the validation periods. The pressure levels that were chosen are 500~hPa or 700~hPa for the upper level, and 925~hPa or 1000~hPa (most often) for the lower level.

Parallel analyses showed that the analogy of circulation is incomplete, and that the geopotential still contains relevant data that can improve the statistical relationship. Therefore, we added a third predictor (still the geopotential height) that the optimizer could use along with the previous parameters. There was no constraint on the predictors, so that the same pressure level could be selected multiple times. Some improvements were found on the score, both for the calibration and the validation periods, confirming that this additional information is beneficial for the quality of the forecast. We then tried with 4 predictors, and so on, up to 8. Every time we added a new predictor to optimize, the score on the calibration period increased, but always more to a smaller extent. However, the score on the validation period dropped after 4 predictors, revealing an over-parametrization of the method, and thus a lack of robustness. We thus found that considering 4 predictors is optimal for our case study, since the gain in CRPSS is significant. It can not be excluded that another number would prevail under other meteorological conditions.

Finally, we added a weighting of these 4 predictors (pressure levels), which is also optimized by GAs. The weighting operates in the combination of the S1 criteria processed on every level, which were previously averaged with equal weights. The role of this new degree of freedom is to give more weight to the levels with greater predictive capacity, and to consider the geopotential variability changes with altitude.

\subsubsection{Which parameters are optimized ?}

The method we finally optimized for the analogy of the atmospheric circulation, based on 4 levels of the geopotential, and that we will name z4, is made of the following degrees of freedom:

\begin{itemize}
	\setlength\itemsep{-4px}
	\item the selection of the pressure levels (4 degrees)
	\item the temporal windows (4 degrees)
	\item the spatial windows (16 degrees)
	\item the weights (4 degrees)
	\item the number of analogues (1 degrees).
\end{itemize}

This sums up to 29 degrees of freedom that are optimize simultaneously.

\subsubsection{Results for the z4 method}

The resulting optimized parameters for z4 vary from one subregion to another. An example of the detailed parameters is provided for the Swiss Chablais in Table \ref{table:params_GA_z4}. The optimized spatial windows are given for every subregion in Figure \ref{fig:spatial_windows_z4}, and the selected pressure levels in Table~\ref{table:levels_GA_z4}.

The resulting CRPSS scores are provided in Table \ref{table:scores} and is in average 35.8 \% in calibration and 35.5 \% in validation. The improvement of the CRPSS score relatively to the reference method on the atmospheric circulation is provided in Table \ref{table:scores_diff} and is in average 15.3 \% in calibration and 9.9 \% in validation. The score was also calculated for three precipitation thresholds: P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_z4}). The gain in score increases with the precipitation threshold: in average, respectively for the different thresholds, 13.3\%, 15.4\% and 29.1\% in calibration and 7.9\%, 11.1\% and 34.5\% for the validation period. The optimized method improves thus even more the forecasts for days with significant precipitation than usual days.

To assess the cross-compatibility of the parameters, we applied those optimized for one subregion to the others. The resulting losses or gains of the CRPSS are displayed in Table \ref{table:crossing_z4_calib} for the calibration period and in Table \ref{table:crossing_z4_valid} for the validation period.

\subsubsection{Analysis}

>>>>

%% Copernicus Publications Manuscript Preparation Template for LaTeX Submissions
%% ---------------------------------
%% This template should be used for copernicus.cls
%% The class file and some style files are bundled in the Copernicus Latex Package which can be downloaded from the different journal webpages.
%% For further assistance please contact the Copernicus Publications at: publications@copernicus.org
%% http://publications.copernicus.org

%% Please use the following documentclass and Journal Abbreviations for Discussion Papers and Final Revised Papers.

%% 2-Column Papers and Discussion Papers
\documentclass[gmd, manuscript]{copernicus}

%% Journal Abbreviations (Please use the same for Discussion Papers and Final Revised Papers)

% Geoscientific Model Development (gmd)
% Hydrology and Earth System Sciences (hess)

%% \usepackage commands included in the copernicus.cls:
%\usepackage[german, english]{babel}
%\usepackage{tabularx}
%\usepackage{cancel}
%\usepackage{multirow}
%\usepackage{supertabular}
%\usepackage{algorithmic}
%\usepackage{algorithm}
%\usepackage{float}
%\usepackage{subfig}
%\usepackage{rotating}

@@

\linenumbers

\title{AtmoSwing (v1.4): Analog Technique Model for Statistical weather forecastING}

% \Author[affil]{given_name}{surname}

\Author[1,2]{Pascal}{Horton}
\Author[1]{Michel}{Jaboyedoff}
\Author[3]{Charles}{Obled}

\affil[1]{University of Lausanne, Lausanne, Switzerland}
\affil[2]{Terranum, Lausanne, Switzerland}
\affil[3]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}

%% The [] brackets identify the author with the corresponding affiliation. 1, 2, 3, etc. should be inserted.

\runningtitle{TEXT}

\runningauthor{TEXT}

\correspondence{Pascal Horton (pascal.horton@alumnil.unil.ch)}

\received{}
\pubdiscuss{} %% only important for two-stage journals
\revised{}
\accepted{}
\published{}

%% These dates will be inserted by Copernicus Publications during the typesetting process.

\firstpage{1}

\maketitle

\begin{abstract}
% TODO: write

\end{abstract}

\introduction  %% \introduction[modified heading if necessary]
% TODO: write

\section{The analogue method}

As AtmoSwing does not rely heavily on one variant of the analogue method, but can implement different parametrization, we gathered here several references of possible implementations as well as the main evolution steps of the analogue method. This latter summarizes the improvements that were brought, as well as discontinued approaches that were found less relevant (such as the use of PCA on the predictors).

\subsection{Principles}

The analogue method is based on the principle that two similar synoptic situations may produce similar local effects \citep{Lorenz1956}. The perfect analogy does not exist, but sufficiently similar situations leading to similar effects can be identified. Thus, two states of the atmosphere that are alike are called analogues \citep{Lorenz1969}. To be relevant, this analogy must be selected by optimizing the following elements:

\begin{itemize}
	\item The analogy variable (the predictor) must contain synoptic information having indirect dependency with the local weather and the target variable (often the precipitation).
	\item The spatial window is the domain on which the analogy variable is considered. The ideal size of this area is one that maximizes useful information.
	\item The temporal window is the hour of day at which we consider the analogy variable. The analogy can be instantaneous (eg. 12~h~UTC) or averaged over a period (eg. 24~h).
	\item The analogy period is the time of year in which similar situations are being sought. Thus, we compare situations with a similar distribution of solar energy \citep{Lorenz1969}.
	\item The analogy criterion, needed to compare the variables on the chosen spatial and temporal windows, is a score used for ranking past situations according to their degree of similarity with the target situation \citep{Bontron2004}.
	\item The ideal number of analogues situations is the best compromise in order to take into account local variability and to maximize useful synoptic information  \citep{Bontron2004}.
\end{itemize}

Because of the chaotic nature of the atmosphere, two analogue situations quickly diverge over time \citep{Lorenz1969}. Thus, the method has strong limitations regarding the temporal extrapolation \citep{Bontron2004}. Numerical models being more capable of simulating the dynamic evolution of the atmosphere, the temporal extrapolation of the synoptic variables is left to them. The search for analogy aims thus at connecting the forecasted synoptic situation with a local predictand (temperature, precipitation ...), which is more difficult to simulate by numerical models.

The analogue method is being used for many years at EDF (\'{E}lectricit\'{e} de France), to build precipitation and temperature scenarios \citep{Desaint2008a}. It is also operational at the Compagnie Nationale du Rh\^{o}ne (CNR, France) and some flood forecasting services (SPC) in France and Switzerland \citep{Marty2010,GarciaHernandez2009b,Horton2012}.

\subsection{Its evolution}

\citet{Lorenz1969} introduced the concept and established the basis of the method. He considered looking for analogues on the geopotential field (at 200, 500 and 850~hPa) with a corrected Euclidean distance averaged on the 3 levels. In addition, the analogue situations were to belong to the same period of the year to be comparable in terms of distribution of solar energy.

The use of the analogue method for operational forecasting of daily precipitation originates in the work of \citet{Duband1970,Duband1974,Duband1981}. It was then designed for operational forecasting at EDF (\'{E}lectricit\'{e} de France) in order to better manage water resources and flood risks. The geopotential height at 700~hPa and 00~h was used for its higher stability than the sea level pressure (SLP) field, and its sensitivity to the atmospheric disturbances \citep{Guilbaud1997}. However, the SLP at 06~h was also used for determining the intensity of precipitation, as well as the temperature at 700~hPa as indicator of the thermal state of the air mass \citep{Duband1974}. The data were then based on 37 radiosounding over Europe and condensed by a principal component analysis. The first 25 analogues on the geopotential at 700~hPa were considered, and multiple local regressions between precipitation, SLP, and the temperature at 700~hPa were established on these analogues before being applied to the target situation \citep{Guilbaud1997}. The archives were split by season to consider comparable situations in terms of distribution of solar energy \citep{Lorenz1969}. This initial rigid division into seasons was then transformed into a moving selection of more or less two months around the target date. The forecast was then performed only on the basis of observations and was temporally extrapolated to the following two days. After a few years, this statistical temporal extrapolation was abandoned in favor of a statistical adaptation using predictors resulting from an global numerical model, allowing a forecast over the following 4~days.

Thereafter, the geopotential was considered at 1000~hPa and 700~hPa and the analogues selection was done in two stages: first according to an Euclidean distance in the space of the principal components of the geopotential field at 700~hPa, and then according to a correlation criterion (on the geopotential field at 700 and 1000~hPa, as well as on the thickness between these two levels) in order to remove days too dissimilar \citep{Guilbaud1997}. The regression approach to determining precipitation was eventually abandoned in favor of the probabilistic forecasting (synthesized by the percentiles 20, 60 and 90~\%), as it is performed today by interpolating linearly over the cumulative empirical distribution of daily precipitation measured at the analogue days \citep{Guilbaud1997,Guilbaud1998}.

\citet{Wilson1980} sought the 20 best analogues on the geopotential field at 500 and 1000~hPa using the Teweles-Wobus (S1) criterion (Eq. \ref{eq:S1}), which allows for a comparison of the gradients and thus an analogy of the atmospheric circulation. \citet{Woodcock1980} used the same criterion on the SLP fields to select 50~analogues in order to forecast maximum daily temperatures. \citet{Yacowar1975} considered the 20 best analogues on the maximum of the sum of correlations on the two fields. This work has demonstrated the best performance of the analogues method compared to regression methods, as well as the interest to search for analogues on two (500 and 1000~hPa) geopotential fields combined \citep{Guilbaud1997}.

\citet{Mandon1985} introduced a second level of analogy and assessed different variables, such as wind, humidity, air temperature, surface temperature of the Mediterranean, the product of wind and the 700~hPa moisture, as well as a second barometric criteria differentiated according to the season. \citet{Vallee1986} continued to work on the second level of analogy and considered the wind at 700~hPa \& 12~h in order to improve heavy precipitation events for a region in France susceptible to southerly flows.

Taking advantage of higher-performance IT tools \citet{Guilbaud1997} stopped using PCA in order to work directly with the raw data interpolated on grids, which was an improvement, especially when considering the S1 criterion (already used for analogues selection by\citealp{Wilson1980} and \citealp{Woodcock1980}) instead of the Euclidean distance. This score gives importance to the similarity of atmospheric circulation rather than absolute values of the pressure field. After comparing this criterion to other criteria from the literature, or combinations of these, \citet{Guilbaud1998} found that S1 is the most efficient. They also pointed out the benefit of using 2 atmospheric levels instead of one (also instead of the thickness), and to also consider 2 temporal windows \citep{Obled2002}. When using multiple predictors, they combined the criteria values calculated on each atmospheric level and each temporal window using an arithmetic mean. Finally, they also suggested using a second level of analogy on lower layers humidity and introduced the Ranked Probability Score \citep{Epstein1969} to assess the forecast quality, which was found to be more relevant that the Brier score \citep{Brier1950}.

\subsection{References implementations}
% TODO: write

\subsection{Datasets}
% TODO: write

\section{Software basics}
% TODO: write

\subsection{Structure}
% TODO: write

\subsection{Modular approach}
% TODO: write

\subsection{Technical specifications}
% TODO: write
% Language and libraries

\subsection{Performance}
% TODO: write

\subsection{Unit tests}
% TODO: write

\section{The forecaster module}
% TODO: write

\section{The viewer module}
% TODO: write

\section{The calibrator module}
% TODO: write

@@

\subsection{Implemented forecasts scores}
% TODO: write

@@

\subsection{Monte-Carlo analysis}

\subsection{Optimization}

\section{The global optimization tools}

@@

\conclusions  %% \conclusions[modified heading if necessary]
% TODO: write

\appendix
\section{}    %% Appendix A

\subsection{}                               %% Appendix A1, A2, etc.

\begin{acknowledgements}
Thanks to Hamid Hussain-Khan of the University of Lausanne for his help and availability, and for the intensive use of the cluster he is in charge of. Thanks to Renaud Marty for his fruitful collaboration over the years.

Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE project which started this research. NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/. Precipitation time series provided by MeteoSwiss. 
\end{acknowledgements}

%% REFERENCES

%% The reference list is compiled as follows:

%\begin{thebibliography}{}
%
%\bibitem[AUTHOR(YEAR)]{LABEL}
%REFERENCE 1
%
%\bibitem[AUTHOR(YEAR)]{LABEL}
%REFERENCE 2
%
%\end{thebibliography}

\bibliographystyle{copernicus}
\bibliography{../_refs/_articles-atmoswing}

%% Since the Copernicus LaTeX package includes the BibTeX style file copernicus.bst,
%% authors experienced with BibTeX only have to include the following two lines:
%%
%% \bibliographystyle{copernicus}
%% \bibliography{example.bib}
%%
%% URLs and DOIs can be entered in your BibTeX file as:
%%
%% URL = {http://www.xyz.org/~jones/idx_g.htm}
%% DOI = {10.5194/xyz}

%% LITERATURE CITATIONS
%%
%% command                        & example result
%% \citet{jones90}|               & Jones et al. (1990)
%% \citep{jones90}|               & (Jones et al., 1990)
%% \citep{jones90,jones93}|       & (Jones et al., 1990, 1993)
%% \citep[p.~32]{jones90}|        & (Jones et al., 1990, p.~32)
%% \citep[e.g.,][]{jones90}|      & (e.g., Jones et al., 1990)
%% \citep[e.g.,][p.~32]{jones90}| & (e.g., Jones et al., 1990, p.~32)
%% \citeauthor{jones90}|          & Jones et al.
%% \citeyear{jones90}|            & 1990

%% FIGURES

%% ONE-COLUMN FIGURES

%%f
%\begin{figure}[t]
%\includegraphics[width=8.3cm]{FILE NAME}
%\caption{TEXT}
%\end{figure}
%
%%% TWO-COLUMN FIGURES
%
%%f
%\begin{figure*}[t]
%\includegraphics[width=12cm]{FILE NAME}
%\caption{TEXT}
%\end{figure*}
%
%
%%% TABLES
%%%
%%% The different columns must be seperated with a & command and should
%%% end with \\ to identify the column brake.
%
%%% ONE-COLUMN TABLE
%
%%t
%\begin{table}[t]
%\caption{TEXT}
%\begin{tabular}{column = lcr}
%\tophline
%
%\middlehline
%
%\bottomhline
%\end{tabular}
%\belowtable{} % Table Footnotes
%\end{table}
%
%%% TWO-COLUMN TABLE
%
%%t
%\begin{table*}[t]
%\caption{TEXT}
%\begin{tabular}{column = lcr}
%\tophline
%
%\middlehline
%
%\bottomhline
%\end{tabular}
%\belowtable{} % Table Footnotes
%\end{table*}
%
%
%%% NUMBERING OF FIGURES AND TABLES
%%%
%%% If figures and tables must be numbered 1a, 1b, etc. the following command
%%% should be inserted before the begin{} command.
%
%\addtocounter{figure}{-1}\renewcommand{\thefigure}{\arabic{figure}a}
%
%
%%% MATHEMATICAL EXPRESSIONS
%
%%% All papers typeset by Copernicus Publications follow the math typesetting regulations
%%% given by the IUPAC Green Book (IUPAC: Quantities, Units and Symbols in Physical Chemistry,
%%% 2nd Edn., Blackwell Science, available at: http://old.iupac.org/publications/books/gbook/green_book_2ed.pdf, 1993).
%%%
%%% Physical quantities/variables are typeset in italic font (t for time, T for Temperature)
%%% Indices which are not defined are typeset in italic font (x, y, z, a, b, c)
%%% Items/objects which are defined are typeset in roman font (Car A, Car B)
%%% Descriptions/specifications which are defined by itself are typeset in roman font (abs, rel, ref, tot, net, ice)
%%% Abbreviations from 2 letters are typeset in roman font (RH, LAI)
%%% Vectors are identified in bold italic font using \vec{x}
%%% Matrices are identified in bold roman font
%%% Multiplication signs are typeset using the LaTeX commands \times (for vector products, grids, and exponential notations) or \cdot
%%% The character * should not be applied as mutliplication sign
%
%
%%% EQUATIONS
%
%%% Single-row equation
%
%\begin{equation}
%
%\end{equation}
%
%%% Multiline equation
%
%\begin{align}
%& 3 + 5 = 8\\
%& 3 + 5 = 8\\
%& 3 + 5 = 8
%\end{align}
%
%
%%% MATRICES
%
%\begin{matrix}
%x & y & z\\
%x & y & z\\
%x & y & z\\
%\end{matrix}
%
%
%%% ALGORITHM
%
%\begin{algorithm}
%\caption{…}
%\label{a1}
%\begin{algorithmic}
%…
%\end{algorithmic}
%\end{algorithm}
%
%
%%% CHEMICAL FORMULAS AND REACTIONS
%
%%% For formulas embedded in the text, please use \chem{}
%
%%% The reaction environment creates labels including the letter R, i.e. (R1), (R2), etc.
%
%\begin{reaction}
%%% \rightarrow should be used for normal (one-way) chemical reactions
%%% \rightleftharpoons should be used for equilibria
%%% \leftrightarrow should be used for resonance structures
%\end{reaction}
%
%
%%% PHYSICAL UNITS
%%%
%%% Please use \unit{} and apply the exponential notation
